---
title: Deployment with RStudio Connect API
output: html_notebook
---

This example is based on the instructions in the [RStudio Connect User Guide](https://docs.rstudio.com/connect/user/cookbook.html#cookbook-deploying). Code for this example can be found on [Github](https://github.com/nwstephens/connect-api).

### 1. Check your environment variables

```{r}
Sys.getenv("CONNECT_API_KEY")
Sys.getenv("CONNECT_SERVER")
```

### 2. Get Placeholder

```{bash}
export DATA='{"name": "shakespeare4", "title": "Shakespeare Word Clouds"}'
curl --silent --show-error -L --max-redirs 0 --fail -X POST \
    -H "Authorization: Key ${CONNECT_API_KEY}" \
    --data "${DATA}" \
    "${CONNECT_SERVER}__api__/v1/experimental/content"
```

#### Set GUID

**Important**: Paste the value for *guid* from the previous step into *CONTENT_GUID* below.

```{r}
Sys.setenv(CONTENT_GUID="04c1194d-9ade-4d5b-9299-49ff0b27b0de")
```

### 3. Bundle

Bundle your content code and the manifest into a tarball.

```{bash}
tar czf bundle.tar.gz faithful/manifest.json faithful/app.R
```

### 4. Upload

Uplad the bundle to RStudio Connect.

```{bash}
curl --silent --show-error -L --max-redirs 0 --fail -X POST \
    -H "Authorization: Key ${CONNECT_API_KEY}" \
    --data-binary @"bundle.tar.gz" \
    "${CONNECT_SERVER}__api__/v1/experimental/content/${CONTENT_GUID}/upload"
```

#### Set Bundle ID

**Important**: Paste the value for *bundle_id* from the previous step into *BUNDLE_ID* below.

```{r}
Sys.setenv(BUNDLE_ID="24973")
```

### 5. Deploy

Deploy the bundle on RStudio Connect. (Note: This code throws an error.)

```{bash}
curl --silent --show-error -L --max-redirs 0 --fail -X POST \
    -H "Authorization: Key ${CONNECT_API_KEY}" \
    --data '{"bundle_id":"'"${BUNDLE_ID}"'"}' \
    "${CONNECT_SERVER}__api__/v1/experimental/content/${CONTENT_GUID}/deploy"
```




