---
title: "RStudio Connect API"
subtitle: "An Example"
---

### Inputs

You will need an API key `CONNECT_API_KEY` and the name of the RStudio Connect server `CONNECT_SERVER` in order to interact with the RStudio Connect API. API Keys are associated with user accounts. They provide roughly the same level of access to RStudio Connect as a user logged in via the browser would have. See section 13.5.1 of the Connect [admin guide](https://docs.rstudio.com/connect/admin/content-management.html#how-this-works-1). The name of the RStudio Connect server will look like: `https://connect.example.com/`.

```{r}
key <- Sys.getenv("CONNECT_API_KEY")
server <- Sys.getenv("CONNECT_SERVER")
```

### Connect API

The `server_settings/r` APIs will return a list of all the installed R versions on RStudio Connect. Pass the `CONNECT_API_KEY` and `CONNECT_SERVER` inputs to see which versions of R are installed.

```{r}
url <- paste0(server, "__api__/v1/server_settings/r")
config <- httr::add_headers(Authorization = paste("Key", key))
httr::GET(url, config)
```


