---
title: Deployment with RStudio Connect API
output: 
  html_notebook:
    toc: true
    toc_float: true
params:
  name: dynamic8
---

This example is based on the instructions in the [RStudio Connect User Guide](https://docs.rstudio.com/connect/user/cookbook.html#cookbook-deploying). Code for this example can be found on [Github](https://github.com/nwstephens/connect-api).

***

### Deployment Process

***

The deployment strategy is to describe the development environment with a manifest and then recreate the environment after it bundle is deployed to RStudio Connect.


#### Overview

1. Describe the environment
    * `Rscript -e 'rsconnect::writeManifest()'`
2. Upload the bundle
    * `tar` -- Bundle all the files
    * `POST /content` -- Retrieve a guid
    * `POST /upload` -- Upload the bundle 
3. Recreate the environment
    * `POST /deploy`

#### Inputs

You will need to supply three inputs. For convenience in later steps, set the inputs as environment variables.

```{r, include = FALSE}
Sys.setenv(NAME = params$name)
Sys.getenv("CONNECT_API_KEY")
Sys.getenv("CONNECT_SERVER")
```

* `CONNECT_API_KEY`: Publishers and admins can request an API key from the RStudio Connect UI. See the [user guide](https://docs.rstudio.com/connect/user/cookbook.html#cookbook-configuring-your-scripts) for more information. 
* `CONNECT_SERVER`: This is the URL for your server. (e.g. "https://connect.example.com/").
* `name`: A unique identifier for the content that is defined by the user.

#### Outputs

Each API returns an identifier that is used in the next API call.

* `guid`: A unique identifier for the content that is defined by the system.
* `bundle_id`: A unique identifier for the version of content that is used in the content URL.
* `task_id`: An identifier for the completed deployment process.

***

### 1. Describe your environment

***

#### Manifest

The manifest defines your development environment. This is done with an R function. The manifest includes things like your R version and package information.

```{r}
rsconnect::writeManifest(appFiles = "app.R")
```

***

### 2. Upload the bundle

***

#### Tar the file

Bundle your content code and the manifest into a tarball.

```{bash}
tar -czf bundle.tar.gz manifest.json app.R
```

#### Get a placeholder

Using the `POST /content` API, retrieve a globally unique identifier that will act as a placeholder for your content.

* Inputs: `CONNECT_API_KEY`, `CONNECT_SERVER`, `name`
* Output: `CONTENT_GUID`

```{bash}
curl --silent --show-error -L --max-redirs 0 --fail -X POST \
    -H "Authorization: Key ${CONNECT_API_KEY}" \
    --data '{"name": "'"${NAME}"'"}' \
    "${CONNECT_SERVER}__api__/v1/experimental/content"
```

#### Upload the bundle

Using the `POST /upload` API, upload the bundle to RStudio Connect.

* Inputs: `CONNECT_API_KEY`, `CONNECT_SERVER`, `CONTENT_GUID`
* Output: `bundle_id`

```{r}
Sys.setenv(CONTENT_GUID="14593e7a-9e8b-47e5-b4a1-a1d7bb3e6a6f")
```

```{bash}
curl --silent --show-error -L --max-redirs 0 --fail -X POST \
    -H "Authorization: Key ${CONNECT_API_KEY}" \
    --data-binary @"bundle.tar.gz" \
    "${CONNECT_SERVER}__api__/v1/experimental/content/${CONTENT_GUID}/upload"
```

***

### 3. Recreate the environment

***

#### Deploy the bundle

Using the `POST /deploy`, deploy the bundle on RStudio Connect.

* Inputs: `CONNECT_API_KEY`, `CONNECT_SERVER`, `CONTENT_GUID`, `BUNDLE_ID`
* Output: `task_id`

```{r}
Sys.setenv(BUNDLE_ID="25048")
```

```{bash}
curl --silent --show-error -L --max-redirs 0 --fail -X POST \
    -H "Authorization: Key ${CONNECT_API_KEY}" \
    --data '{"bundle_id":"'"${BUNDLE_ID}"'"}' \
    "${CONNECT_SERVER}__api__/v1/experimental/content/${CONTENT_GUID}/deploy"
```

#### Verify the deployment

Verify that the bundle finished. Use `first` to define what part of the output you would like to capture (`first=0` by default).

```{r}
Sys.setenv(TASK="VSM5rrSv0kkOStMn")
```

```{bash}
curl --silent --show-error -L --max-redirs 0 --fail \
    -H "Authorization: Key ${CONNECT_API_KEY}" \
    "${CONNECT_SERVER}__api__/v1/experimental/tasks/${TASK}?wait=1&first=0"
```

#### Open in RStudio Connect

Congratulations! Click the links to open the deployed assets in RStudio Connect.

* [Open in UI](`r paste0(Sys.getenv("CONNECT_SERVER"), "connect/#/apps/", Sys.getenv("CONTENT_GUID"))`)
* [Open solo](`r paste0(Sys.getenv("CONNECT_SERVER"), "content/", Sys.getenv("CONTENT_GUID"))`)


